\begin{question}
    In the Dutch Roll approximation, and under the assumption that off-diagonal elements in an aircraft's inertia matrix are negligible, the state space $\mathbf{A}_{lat}$ and $\mathbf{B}_{lat}$ matrices and state $\mathbf{x}_{lat}$ become:
    \begin{align*}
        \mathbf{x}_{dr} =
        \begin{bmatrix}
            \Delta v \\
            \Delta r
        \end{bmatrix}
        \quad
        \mathbf{A}_{dr} = 
        \begin{bmatrix}
            Y_v/m & -u_0 \\
            N_v/I_z & N_r/I_z
        \end{bmatrix}
        \quad
        \mathbf{B}_{dr} =
        \begin{bmatrix}
            0 & Y_{\delta_r}/m \\
            N_{\delta_a}/I_z & N_{\delta_r}/I_z
        \end{bmatrix}
    \end{align*}
    Consider implementing a yaw damper control law to improve the damping ratio of the Dutch Roll mode. This control law applies to the rudder only, and is $\Delta \delta_r = -k \Delta r$, $\Delta \delta_a = 0$.
    \begin{enumerate}
        \item Write an expression to calculate $\mathbf{u} = [\Delta \delta_a, \Delta \delta_r]^T$ in the form $\mathbf{u} = -\mathbf{K} \mathbf{x}_{dr}$, where $\mathbf{K}$ is a matrix of control gains. Then, find the closed-loop dynamics matrix $\mathbf{A}_{dr,cl}$ using $\mathbf{A}_{dr,cl} = \mathbf{A}_{dr} - \mathbf{B}_{dr} \mathbf{K}$
        \item Write out the characteristic equation for the eigenvalues $\lambda$ of $\mathbf{A}_{dr,cl}$, and then solve for $k$ in terms of $\lambda$ and variables in $\mathbf{A}_{dr}$ and $\mathbf{B}_{dr}$.
        \item A large jet transport has the following $\mathbf{A}_{dr}$ and $\mathbf{B}_{dr}$ matrices:
        \begin{align*}
            \mathbf{A}_{dr} = 
            \begin{bmatrix}
                -0.056 & -730 \\
                0.0012 & -0.15
            \end{bmatrix}
            \quad
            \mathbf{B}_{dr} =
            \begin{bmatrix}
                0 & 5.5 \\
                0.004 & -0.47
            \end{bmatrix}
        \end{align*}
        What is the damping ratio $\zeta$ of the Dutch Roll mode without the yaw damper in place?

    \item Find the transfer function, $G_{\Delta v \delta_r}(s)$, relating the rudder deflection to sideslip velocity using the numerical values above.

        \item We wish to increase the damping ratio of the Dutch Roll mode using the yaw damper control law. If $\zeta = 0.7$ and $\omega_n = 0.9656$ rad/s, what value of $k$ is required in the control law? (Note: A calculation using your result from Part 2 will likely give you a value of $k$ that has a small imaginary part. Ignore the imaginary part in your answer, as it is an artifact of the way this problem was set up.)
        \item The jet is capable of $\Delta \delta_r = \pm 25^\circ$. Using the value of $k$ found in the previous part, what is the largest $\Delta r$ that the yaw damper can handle and still achieve $\zeta = 0.7$ for the Dutch Roll mode? 
    \end{enumerate}
\end{question}
